A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-30 paper.tex
Work in progress
Abstract double check: removed dash added from a (PDF document) copy paste.

Several bio-inspired algorithms use population evolution as analogies of
na-ture. In this paper, we present an algorithm inspired by the biological
Life-Cycle of animal species, which consists of several stages: birth, growth,
re-production, and death. As in nature, we intend to execute all these stages
in parallel and asynchronously on a population that evolves constantly. From
the ground up, we designed the algorithm as a cloud-native solution using the
cloud available resources to divide the processing workload, among several
computers or running the algorithm as a cloud service. The algorithm works
concurrently and asynchronously on a constantly evolving population, using
different computers (or containers) independently, eliminating waiting times
between processes. This algorithm seeks to imitate the natural life cycle,
where new individuals are born at any moment and mature over time, where they
age and suffer mutations throughout their lives. In reproduction, couples match
by mutual attraction, where they may have offspring. Death can happen to
everyone: from a newborn to an aged adult, where the individual's fitness will
impact their longevity. As a proof-of-concept, we implemented the algo-rithm
with Docker containers by solving the OneMax problem comparing it with a basic
(sequential) GA algorithm, where it showed favorable and prom-ising results.

>>>>

Several bio-inspired algorithms use population evolution as analogies of
nature. In this paper, we present an algorithm inspired by the biological
Life-Cycle of animal species, which consists of several stages: birth, growth,
reproduction, and death. As in nature, we intend to execute all these stages in
parallel and asynchronously on a population that evolves constantly. From the
ground up, we designed the algorithm as a cloud-native solution using the cloud
available resources to divide the processing workload among several computers
or running the algorithm as a cloud service. The algorithm works concurrently
and asynchronously on a constantly evolving population, using different
computers (or containers) independently, eliminating waiting times between
processes. This algorithm seeks to imitate the natural life cycle, where new
individuals are born at any moment and mature over time, where they age and
suffer mutations throughout their lives. In reproduction, couples match by
mutual attraction, where they may have offspring. Death can happen to everyone:
from a newborn to an aged adult, where the individual's fitness will impact
their longevity. As a proof-of-concept, we implemented the algorithm with
Docker containers by solving the OneMax problem comparing it with a basic
(sequential) GA algorithm, where it showed favorable and promising results.
